---
title: "Research and Development (R&D) and Innovation: Australia"
output: 
    orientation: column
    vertical_layout: fill
    runtime: shiny
    social: menu
    source_code: embed 
---

```{r setup, include=FALSE}
library(plotly)
library(shiny)
library(ggplot2)
library(dplyr)
library(forcats)
library(tidyr)
library(stringr)
library(scales)

#Importing data
GOV_RD <- read.csv("Gover_Resc_RD.csv", sep = ",")

#Changing GOV_RD to long
GOV_RD_Long <- gather(GOV_RD,"Year","Value",X2008.09:X2018.19)

#Strip x from "x2008.09" in year variable
GOV_RD_Long$Year <- as.factor(str_replace(GOV_RD_Long$Year,"\\w",""))

#Label the Year range
GOV_RD_Long$Year <- factor(GOV_RD_Long$Year, labels = c("2008-09", "2011-12", "2012-13", 
                                                        "2014-15", "2016-17", "2018-19"))

#Removing white space from Values
GOV_RD_Long$Value <- (str_replace(GOV_RD_Long$Value," ",""))

#Changing Value to numeric
GOV_RD_Long$Value <- as.numeric(GOV_RD_Long$Value)

##Label Description range
GOV_RD_Long$Description <- as.factor(GOV_RD_Long$Description)

#Spread the numerical values(providers)
GOV_RD_Sp <- spread(GOV_RD_Long, "Provider", "Value")

#Importing data
PRV_RD <- read.csv2("PriveateNGO_RD.csv", sep = ",")

#Changing GOV_RD to long
PRV_RD_Long <- gather(PRV_RD,"Year","Value",X2008.09:X2018.19)

#Strip x from "x2008.09" in year variable
PRV_RD_Long$Year <- as.factor(str_replace(PRV_RD_Long$Year,"\\w",""))

#Label the Year range
PRV_RD_Long$Year <- factor(PRV_RD_Long$Year, labels = c("2008-09", "2011-12", "2012-13", 
                                                        "2014-15", "2016-17", "2018-19"))

#Removing white space from Values
PRV_RD_Long$Value <- (str_replace(PRV_RD_Long$Value," ",""))

#Changing Value to numeric
PRV_RD_Long$Value <- as.numeric(PRV_RD_Long$Value)

##Label the Description range
PRV_RD_Long$Description <- as.factor(PRV_RD_Long$Description)

#Importing data
GOV_LOCA <- read.csv("GOVERD, by location of expenditure.csv", sep = ",")
GOV_LOCA$Location_GOVERD <- factor(GOV_LOCA$Location_GOVERD, levels = c("VIC", "NSW", "QLD", "SA", 
                                                                        "ACT", "WA","TAS", "NT", "Overseas"),
                                   labels = c("VIC", "NSW", "QLD", "SA",
                                              "ACT", "WA","TAS", "NT", "Overseas"))
#Import Data
PRV_LOCA <- read.csv("PNPERD, top 5 locations.csv", sep = ",")
PRV_LOCA$Locations_PNPERD <- factor(PRV_LOCA$Locations_PNPERD, levels = c("VIC","NSW", "WA", "QLD","Overseas"),
                                    labels = c("VIC","NSW", "WA", "QLD", "Overseas"))
#Innovation Import Data
inov_act <- read.csv("Summary of innovative activity-AU.csv", sep = ",")
inov_act$Industry <- as.factor(inov_act$Industry)
inov_act$Innovation_Implemented <- as.numeric(inov_act$Innovation_Implemented)
inov_act$In_Development <- as.numeric(inov_act$In_Development)
inov_act$Innovative_Activity <- as.numeric(inov_act$Innovative_Activity)
inov_act$Abandoned <- as.numeric(inov_act$Abandoned)
Innovation.Status = c("Innovation_Implemented", "In_Development", "Innovative_Activity", "Abandoned")

#Innovation area Import Data
area_inov <- read.csv("Business_intro_New.csv", sep = ",")
area_inov[2:17] <- sapply(area_inov[2:17],as.numeric)
area_inov$Innovation_Type <- factor(area_inov$Innovation_Type, levels = c("Goods", "Services", "Both"), labels = c("Goods", "Services", "Both"))
Industry.Type = c( "AFF",	"AFS",	"ARS",	"ASS",	"CON",	"EGWW",	"FIS",	"HCSA",	"IMT",	"MANU",	"MIN", "Others",	"PST",	"RHRE",	"RT",	"TPW",	"WT")

#Summary
#Status Import Data
inov_stat <- read.csv("Innovation_Status2012-17.csv", sep = ",")
inov_stat$Innovation_Status <- as.factor(inov_stat$Innovation_Status)
                                         
#Benefits Import Data
benefit <- read.csv("Benefits_Innov_Selected2016-17.csv", sep = ",")
benefit$Result <- as.factor(benefit$Result)
benefit$Area <- as.factor(benefit$Area)
benefit$Value <- as.numeric(benefit$Value)
```

# R&D Expenditure

Column {data-width=600, .tabset}
-----------------------------------------------------------------------

### **Government**

```{r}
p <- ggplot(data = GOV_RD_Long, 
            aes(x = Year, y = Value, group = Description)) +
  geom_line(aes(color = Description)) +
  geom_point(aes(color = Description)) +
  facet_wrap(~Provider,  ncol=1, strip.position = "left") +
  labs( x = "Year", y = "$ in Million",
        title = "Government Expenditure in R&D 2008-2019", 
        caption = "SOURCE:Source: Australian Bureau of Statistics, 
        Research and Experimental Development, 
        Government and Private Non-Profit Organisations, Australia 2018-19 financial year") + 
  scale_y_continuous(limits = c(1000,3000)) +
  scale_color_brewer(palette="Dark2") + 
  theme_minimal() 

p <- ggplotly(p)
p

p
```

### **Private**

```{r}
p1 <- ggplot(data = PRV_RD_Long, 
            aes(x = Year, y = Value, group = Description)) +
  geom_line(aes(color = Description)) +
  geom_point(aes(color = Description)) +

  labs( x = "Year", y = "$ in Million",
        title = "Private and Non Profit Expenditure in R&D 
        2008-2019", 
        caption = "SOURCE:Source: Australian Bureau of Statistics, 
        Research and Experimental Development, 
        Government and Private Non-Profit Organisations, Australia 2018-19 financial year") + 
  scale_y_continuous(limits = c(500,1500)) +
  scale_color_brewer(palette="Dark2") + 
  theme_minimal()

p1 <- ggplotly(p1)

p1
```

Column {data-width=400}
-----------------------------------------------------------------------

### **Location (Government)**

```{r}
p2 <- ggplot(data = GOV_LOCA, 
            aes(x = Location_GOVERD, y = Value, fill = Year)) +
  geom_bar(stat = "identity", color="black", width=0.5, position=position_dodge()) + 
  theme_minimal() +  
  labs(x = "Location", y = "$ in Million",
       title = "Government Expenditure in R&D by Location 
       (2016 -2019)",
       caption = "SOURCE:Source: Australian Bureau of Statistics, 
       Research and Experimental Development, 
       Government and Private Non-Profit Organisations, Australia 2018-19 financial year") + 
  scale_fill_brewer(palette="Dark1") 

p2 <- ggplotly(p2)

p2
```

### **Location (Private)**

```{r}
p3 <- ggplot(data = PRV_LOCA, 
            aes(x = Locations_PNPERD, y = Value, fill = Year)) +
  geom_bar(stat = "identity", color="black", width=0.5, position=position_dodge()) + 
  theme_minimal() +  
  labs(x = "Location", y = "$ in Million",
       title = "Private Expenditure in R&D by Location 
       (2016 -2019)",
       caption = "SOURCE:Source: Australian Bureau of Statistics, 
       Research and Experimental Development, 
       Government and Private Non-Profit Organisations, Australia 2018-19 financial year") + 
  scale_fill_brewer(palette="Reds") 

p3 <- ggplotly(p3)

p3
```
# Innovation

Column {.sidebar data-width=200}
-----------------------------------------------------------------------
```{r}

selectInput("Innovation_Status", label = "Select Innovation Activity:", choices = Innovation.Status)

selectInput("Industry_Type", label = "Select Industry:", choices = Industry.Type)

```

Column {data-width=500}
-----------------------------------------------------------------------

### **Innovation Activity**

```{r}
renderPlotly({
p4 <- plot_ly(inov_act, x = ~inov_act[[input$Innovation_Status]], y = ~Industry , type = 'bar', orientation = 'h', text = "%",
        marker = list(color = "rgb(121, 195, 174)",
                      line = list(color = "rgb(20, 20, 20)",
                                  width = 1.5)))
p4 <- p4 %>% layout(title = "Innovation Activity in Australian Business (2016-17)",
         xaxis = list(title = "%"),
         yaxis = list(title = ""))
})

```

Column {data-width=300}
-----------------------------------------------------------------------

### **Innovation Type**

```{r}
renderPlotly({
p5 <- plot_ly(area_inov, x = ~Innovation_Type, y = ~area_inov[[input$Industry_Type]], type = 'bar', text = "%",
        marker = list(color = "rgb(221, 119, 85)",
                      line = list(color = "rgb(20, 20, 20)",
                                  width = 1.5)))
p5 <- p5 %>% layout(title = "Goods and Services Innovation, 
                    by Industry (2016-17)",
         xaxis = list(title = ""),
         yaxis = list(title = "%"))
})

```

### **KEY**

<p><font color=darkgreen> 
AFF:  Agriculture, Forestry and Fishing

AFS:  Accommodation and Food Services

ARS:  Arts and Recreation Services

ASS:  Administrative and Support Services

CON:  Construction

EGWW: Electricity, Gas, Water and Waste Services

FIS:  Financial and Insurance Services

HCSA: Health Care and Social Assistance

IMT:  Information Media and Telecommunications

MANU: Manufacturing

MIN:  Mining

PST:  Professional, Scientific and Technical Services

RHRE: Rental, Hiring and Real Estate Services

RT:   Retail Trade

TPW:  Transport, Postal and Warehousing

WT:   Wholesale Trade </font> </p>

# Summary

Column {data-width=600, .tabset}
-----------------------------------------------------------------------
  
### **Status**
```{r}
p6 <- ggplot(data = inov_stat, 
             aes(x=Year, y=Value, fill = Innovation_Status)) +
  geom_bar(stat='identity', width=1) + theme_minimal() +
  facet_wrap(~Innovation_Status) + scale_y_continuous(labels =  scales::percent) +
  
  labs(x = "Innovation Status/Type", 
       title = "Summary of Innovation in Australian Business (2013-2017)",
       caption = "SOURCE:Source: Australian Bureau of Statistics, 
       Research and Experimental Development, 
       Government and Private Non-Profit Organisations, Australia 2018-19 financial year") + 
  scale_fill_brewer(palette="Set1")
p6 <- (ggplotly(p6))

p6
```

### **Benefits**

```{r}
p7 <- ggplot(data = benefit, 
             aes(x=Area, y=Value, fill = Area)) +
  geom_bar(stat='identity', color = "black", width=0.9) + theme_minimal() +
  facet_wrap(~Result) + scale_y_continuous(labels =  scales::percent) +
  
  labs(x = "Business Type", 
       title = "Selected Benefits of Innovation (2016-2017)",
       caption = "SOURCE:Australian Bureau of Statistics, 
       Research and Experimental Development, 
       Government and Private Non-Profit Organisations, Australia 2018-19 financial year") + 
  scale_fill_brewer(palette="Set3")
p7 <- (ggplotly(p7))

p7
```

Column {data-width=400}
-----------------------------------------------------------------------
  
### Summary
```{r}
BillionForm <- dollar_format(prefix = "$",suffix="B")
valueBox(BillionForm(3.33), caption = paste("Expenditure on R&D performed by Australian government organisations during the 2018-19 financial year"), icon = "fa-money",col="rgb(46, 113, 42)")

```

### Source and Reference

```{r}
BillionForm <- dollar_format(prefix = "$",suffix="B")
valueBox(BillionForm(3), caption = paste("The value of support for R&D through the tax incentive scheme.*Business innovations are mainly supported by the government through the R&D tax incentive scheme"), icon = "fa-bank",color = "rgb(75, 89, 202)") 
```

### Value

```{r}
BillionForm <- dollar_format(prefix = "$",suffix="B")
valueBox(BillionForm(1.27), caption = paste("Expenditure on R&D performed by Australian private non-profit (PNP) organisations during the 2018-19 financial year"), icon = "fa-briefcase",col="rgb(0, 53, 128)")
```

### **Sources and References**

<p><font color=blue>Sources:
  
1. Australian Bureau of Statistics, Research and Experimental Development, Government and Private Non-Profit Organisations,Reference period 2018-19 financial year (Released Date: 19/06/2020), https://www.abs.gov.au/
  
2. Australian Bureau of Statistics, Innovation in Australian Business, Reference period
2016-17 financial year (Released Date: 19/07/2018) </font>

<font color=darkred>References:
  
1. Grant Australia the opportunity to innovate, UNSW Newsroom website, https://newsroom.unsw.edu.au/news/business-law/grant-australia-opportunity-innovate

2. Support for businesses in Australia, Australian Government Business, https://business.gov.au/
  
3. RDocumentation, https://www.rdocumentation.org/
  
4. ggplot2 Reference, https://ggplot2.tidyverse.org/ </font></p>
  